Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-24 paper/main.tex
abstract, conclusion, etc.

\begin{abstract}
Abstract
\end{abstract}

@@

>>>>

\begin{abstract}
As dynamically-typed languages continue to grow in popularity, especially
among beginning programmers, there is an increased need to provide precise
localization for defects. In many instances, such localization is
ambiguous: multiple program locations are equally formally implicated in
the bug, but not all are equally relevant to human programmers. We propose
a scalable fault localization approach for dynamic languages that agrees
with human judgments. We base our approach on a combination of static,
dynamic, and contextual features, guided by machine learning. We evaluate
our approach on over 270,000 diverse real user instances from the popular
PythonTutor.com website. We find that our approach is scalable, general,
and quite accurate: up to 79\% for top-three responses, compared to 45\%
for the default interpreter. 
\end{abstract}

@@

We present an approach for accurately localizing type errors in
off-the-shelf beginner-written Python programs. Our approach makes use of a
combination of static, dynamic and contextual features. Static features,
such as syntactic forms and expression sizes, are a particularly powerful
heuristic for novice programmer defects. Dynamic features can both 
implicate relevant terms (partial typing information) and rule out
irrelevant program regions (slicing). Contextual features allow our
approach to gain the benefits of precise AST- or CFG-style information
while retaining the scalable performance of a linear representation. 
We use off-the-shelf machine learning to accurately combine those disparate
features in a way that captures and models human judgments of ground-truth
correct answers --- a notion that is especially relevant when multiple 
program locations are equally formally implicated but not equally useful to
the user.

We evaluate our approach with respect to historical user defects and fixes.
All of the feature categories (static, dynamic, and contextual) were
relevant to success, as measured by multiple analyses (Gini, ANOVA and
leave-one-out). Our evaluation demonstrated significant scalability and
generality: our 270,000 instances were both an order-of-magnitude more
numerous than similar related work and measurably more diverse. Ultimately,
our approach was quite accurate, implicating the correct program location
60--79\% of the time compared to the Python interpreter's 45\% accuracy.
